Linting Linearity in Core/System FC

### 2023-09-29 proposal.tex
Almost closed implemenetation section

The key idea to computing the usage environment of multiple variables that use
themselves in their definition body is to perform the computation in two separate passes. First,
calculate a naive environment by emitting free variables multiplicities as usual
while treating the recursive-let bound variables as free ones. Second, pass the
variables names and their corresponding naive environment as input to
algorithm~\ref{computeRecUsages} to get a final usage environment. Intuitively,
the algorithm, for each recursive binder, iterates over all (initially naive) usage
environments and substitutes the recursive binder by the corresponding usage
environment, scaled up by the amount of times that recursive binder is used in
the environment being updated.

>>>>

The key idea to computing the usage environment of multiple variables that use
themselves in their definition body is to perform the computation in two separate passes. First,
calculate a naive environment by emitting free variables multiplicities as usual
while treating the recursive-let bound variables as free ones. Second, pass the
variables names and their corresponding naive environment as input to
Algorithm~\ref{computeRecUsages} to get a final usage environment. Intuitively,
the algorithm, for each recursive binder, iterates over all (initially naive) usage
environments and substitutes the recursive binder by the corresponding usage
environment, scaled up by the amount of times that recursive binder is used in
the environment being updated.
